---
title: "p8105_hw6_yc4198"
author: "Yining Chen"
date: "2022-12-03"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(purrr)
library(modelr)
```

## Question 2

### Data cleaning
```{r,warning=FALSE,message=FALSE}
homicide <- read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")

homicide <- homicide%>%
  janitor::clean_names()%>%
  mutate(city_state=str_c(city, ",",state),
         resolved = as.numeric(disposition == "Closed by arrest"),
         victim_age = as.numeric(victim_age))%>%
  filter(victim_race== "White"|victim_race== "Black")%>%
  filter(city_state != "Dallas,TX"&city_state != "Phoenix,AZ"&city_state != "Kansas City,MO"& city_state != "Tulsa,AL")
```

### Fit the model for Baltimore
```{r}
baltimore <- homicide%>%filter(city_state == "Baltimore,MD")%>%
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_race = fct_relevel(victim_race, "White")) %>% 
  select(resolved, victim_age, victim_race, victim_sex)

glm1 <- glm(resolved ~ victim_age+victim_sex+victim_race, data = baltimore,family = binomial())

glm1 %>% broom::tidy() %>%
  mutate(OR = exp(estimate),
         lower_CI = OR - qnorm(0.95)*std.error,
         upper_CI = OR + qnorm(0.95)*std.error,
         term = str_replace(term, "victim_sex", "Victim Sex: "))%>%
  filter(term == "victim_sexMale")%>%
    select(term, OR, lower_CI,upper_CI)%>%
  knitr::kable(digits = 3)
```

### Run glm for each city
```{r}
each_city = 
  homicide %>%
  select(city_state,resolved, victim_age, victim_race, victim_sex)%>%
  nest(data = -city_state)%>%
  mutate(
    fit  = map(.x = data,  ~glm(resolved ~ victim_race + victim_sex + victim_age, data = .x, family = "binomial")),
    result = map(fit, broom::tidy)) %>%
    unnest(result) %>% 
  filter(term == "victim_sexMale")%>%
    mutate(OR = exp(estimate),
         lower_CI = OR - qnorm(0.95)*std.error,
         upper_CI = OR + qnorm(0.95)*std.error)%>%
    select(city_state, OR, lower_CI,upper_CI)%>%
  knitr::kable(digits = 3)
```

```{r}
each_city%>% 
  ggplot(aes(x=OR,y = reorder(city_state, -OR))) +
  geom_point(color="red",size=1) +
  geom_errorbar(aes(xmin = lower_CI, xmax = upper_CI)) +  
  theme(axis.text.x = element_text(size = 8,vjust = 0.5, hjust = 1),axis.text.y = element_text(size=5.5))+
  ylab("City")+
  xlab("Odds Ratio")+
  ggtitle("Estimated ORs and CIs for each city.")
```

## Question 3

### Load and clean the data for regression analysis 
```{r,warning=FALSE,message=FALSE}
birthweight = read_csv("data/birthweight.csv") %>%
  janitor::clean_names()%>%
  drop_na()%>%
 mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
  ) 
  
```

### Propose a regression model for birthweight. 

I started with a full model with all 19 variables as explanatory variables and birthweight as the response variable. Then I used a stepwise model selection,which is a combination of forward and backward selections. This is to build regression model from a set of candidate predictor variables by entering and removing predictors based on p values, until there is no variable left to enter or remove any more.
 
The final model includes the following variables:
babysex: baby’s sex (male = 1, female = 2)
bhead: baby’s head circumference at birth (centimeters)
blength: baby’s length at birth (centimeteres)
delwt: mother’s weight at delivery (pounds)
fincome: family monthly income (in hundreds, rounded)
gaweeks: gestational age in weeks
mheight: mother’s height (inches)
mrace: mother’s race (1 = White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other)
parity: number of live births prior to this pregnancy
ppwt: mother’s pre-pregnancy weight (pounds)
smoken: average number of cigarettes smoked per day during pregnancy


```{r}
mymod <-lm(bwt ~., data = birthweight)
step.model <- step(mymod,direction = "both") 
step.model%>%broom::tidy()
```
### Diagnostics
```{r}
birthweight %>% 
  add_predictions(step.model) %>% 
  add_residuals(step.model) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5,color="red") +
  labs(
    x = "Fitted Values",
    y = "Residuals",
    title = "Residuals vs. Fitted Values"
  )+theme_minimal()
```

### Compare models
```{r}
mod1 <- lm(bwt ~ blength+gaweeks, data = birthweight)
mod2 <- lm(bwt ~ bhead+blength+babysex+bhead*blength+blength*babysex+bhead*babysex+bhead*babysex*blength, data = birthweight)
```

```{r}

```

